R-LIME: LIME法における矩形制約と最適化

### 2024-04-09 paper/paper.tex
modify details of paper

Anchor maximizes the coverage of region $A$
as long as the probability of the output of the black-box classifier $f$ matching $f(x)$
within $A$ exceeds a given threshold $\tau$.
The proposed method, on the other hand, learns an linear classifier $g$
within the rectangular region $A$ and maximizes the coverage of $A$
under lower constraints on the accuracy of $g$.
We modify the Anchor's definition of accuracy in \cref{eq:anchor_def_prec}
as follows:
\begin{equation}
  \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
\end{equation}
where $G$ is the set of possible linear classifiers.
By solving the optimization problem in \cref{eq:main_problem}
under the modified accuracy definition in \cref{eq:def_prec},
we can select the rule that enables explanation with high accuracy and generality.
% The characteristics of R-LIME are listed below:
% \begin{itemize}
% 	\item The approximation region is optimal and interpretable.
% 	\item The dataset is not directly accessed, and only the distribution is utilized.
% 	\item The number of samples is dynamically determined
% 	      based on the estimated accuracy without the need for predefining it.
% \end{itemize}

@@

  \foreach \alg in {2,3,4}{%
      \begin{algorithm}[p]
        \small
        \input{tex/alg\alg}
      \end{algorithm}
    }
}
The algorithm of R-LIME
is mainly based on that used in Anchor\cite{ribeiro2018anchors}.
For non-convex optimization problems like \cref{eq:main_problem},
greedy search are often used.
However,
greedy methods tend to converge to local optima, and to address this,
R-LIME utilizes beam search,
which selects multiple candidates at each iteration.
The pseudo code is shown in \cref{alg:greedy_search}.

\subsubsection{Generation of New Candidate Rules}
To generate new candidate rules,
one additional predicate is added to each of the $B$ candidate rules
selected in the previous iteration.
The pseudo code is shown in \cref{alg:generate_cands}.
$T(x)$ is the set of attribute-value pairs (predicates) that are true for $x$,
and $T(x)\setminus A$ is the set of predicates in $T(x)$ not included in rule $A$.

\subsubsection{Selection of Candidate Rules with Maximum Accuracy}
Given the set of candidate rules $\cands$,
the algorithm selects the top $B$ candidates with the highest accuracy.
This problem can be formulated
as best arm identification in the multi-armed bandit framework.
Each candidate rule $A_i\in\cands$ is considered as an arm,
and its accuracy $\Prec(A_i)$ is considered as the distribution of rewards.
By sampling $z\sim\mathcal{D}(\cdot|A_i)$
and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial,
the algorithm updates $g_i$ using the sampled perturbation vector $z$
and the pseudo-label $f(z)$ after each trial.
To efficiently select the rule (arm) with the highest accuracy,
we employ the KL-LUCB algorithm \cite{kaufmann2013information}.
The pseudo code is shown in \cref{alg:best_cands}.
For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
\begin{equation}
  P(\underset{A\in\cands}{\min}\Prec(A)\ge
  \underset{A'\in\mathcal{A}}{\min}\Prec(A')-\epsilon)\ge1-\delta.
\end{equation}
However,
the KL-LUCB algorithm assumes that the reward distribution for each arm
remains unchanged,
while our method updates the classifier $g_i$ with each sampling,
which may not satisfy this assumption.
This issue is discussed further in \cref{sec:reward}.

\subsubsection{Selection of the Rule with Maximum Coverage Meeting the Constraint}
To satisfy the constraint imposed by \cref{eq:const_prec}, rule $A$ needs to fulfill the lower bound constraint:
\begin{equation}
  \Prec_{l}(A,\delta)>\tau
  \label{eq:stop_condition}
\end{equation}
where $\Prec_{l}(A,\delta)$ is the lower limit of
the $100(1-\delta)$\% confidence interval for $\Prec(A)$.
If the received set of candidate rules, $\mathcal{A}$,
includes a rule satisfying \cref{eq:stop_condition},
the one with the maximum coverage among them is selected,
and the iteration is terminated.
If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop_condition},
it returns \textbf{null},
and proceeds to the next iteration.
The pseudo code is presented in \cref{alg:largest_valid_cand}.

>>>>

Anchor maximizes the coverage of region $A$
as long as the probability of the output of the black-box classifier $f$ matching $f(x)$
within $A$ exceeds a given threshold $\tau$.
The proposed method, on the other hand, learns an linear classifier $g$
within the rectangular region $A$ and maximizes the coverage of $A$
under lower constraints on the accuracy of $g$.
We modify the Anchor's definition of accuracy in \cref{eq:anchor_def_prec}
as follows:
\begin{equation}
  \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
\end{equation}
where $G$ is the set of possible linear classifiers.
By solving the optimization problem in \cref{eq:main_problem}
under the modified accuracy definition in \cref{eq:def_prec},
we can select the rule that enables explanation with high accuracy and generality.

@@

  \foreach \alg in {2,3,4}{%
      \begin{algorithm}[p]
        \small
        \input{tex/alg\alg}
      \end{algorithm}
    }
}
The algorithm of R-LIME
is mainly based on that used in Anchor\cite{ribeiro2018anchors}.
For non-convex optimization problems like \cref{eq:main_problem},
greedy search are often used.
However,
greedy methods tend to converge to local optima, and to address this,
R-LIME uses beam search,
which selects multiple candidates at each iteration.
The pseudo-code is shown in \cref{alg:greedy_search}.

\subsubsection{Generation of New Candidate Rules}
To generate new candidate rules,
one additional predicate is added to each of the $B$ candidate rules
selected in the previous iteration.
The pseudo-code is shown in \cref{alg:generate_cands}.
$T(x)$ is the set of predicates $\{a_1,\dots,a_m\}$,
where $a_i(z)$ evaluates to true when $z_i=x_i$ and false otherwise,
and $T(x)\setminus A$ is the set of predicates in $T(x)$ not included in rule $A$.

\subsubsection{Selection of Candidate Rules with Maximum Accuracy}
Given the set of candidate rules $\cands$,
the algorithm selects the top $B$ candidates with the highest accuracy.
This problem can be formulated
as best arm identification in the multi-armed bandit framework.
Each candidate rule $A_i\in\cands$ is considered as an arm,
and reward of arm $a_i$ follows a Bernoulli distribution
with $P(X=1)=\Prec(A_i)$.
By sampling $z\sim\mathcal{D}(\cdot|A_i)$
and obtaining the reward $\mathbbm{1}_{f(z)=g_i(z)}$ for each trial,
the algorithm updates $g_i$ using $z$ and $f(z)$ after each trial.
To efficiently select the rule (arm) with the highest accuracy,
we employ the KL-LUCB algorithm \cite{kaufmann2013information}.
The pseudo-code is shown in \cref{alg:best_cands}.
For tolerance $\epsilon\in[0,1]$, the KL-LUCB algorithm guarantees below:
\begin{equation}
  P(\underset{A\in\cands}{\min}\Prec(A)\ge
  \underset{A'\in\mathcal{A}}{\min}\Prec(A')-\epsilon)\ge1-\delta.
\end{equation}
However,
the KL-LUCB algorithm assumes that the reward distribution for each arm
remains unchanged,
while our method updates the classifier $g_i$ with each sampling,
which may not satisfy this assumption.
This issue is discussed further in \cref{sec:reward}.

\subsubsection{Selection of the Rule with Maximum Coverage Meeting the Constraint}
To satisfy the constraint imposed by \cref{eq:const_prec}, rule $A$ needs to fulfill the lower bound constraint:
\begin{equation}
  \Prec_{l}(A,\delta)>\tau
  \label{eq:stop_condition}
\end{equation}
where $\Prec_{l}(A,\delta)$ is the lower limit of
the $100(1-\delta)$\% confidence interval for $\Prec(A)$.
If the received set of candidate rules, $\mathcal{A}$,
includes a rule satisfying \cref{eq:stop_condition},
the one with the maximum coverage among them is selected,
and the iteration is terminated.
If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop_condition},
it returns \textbf{null},
and proceeds to the next iteration.
The pseudo-code is presented in \cref{alg:largest_valid_cand}.
